Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores. II. Nanoflare Trains

### 2016-10-18 tex/paper.tex
final tweaks before revisions submitted

\documentclass[preprint,linenumbers]{aastex}

@@

		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated. Here, the bin widths are calculated according to the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}}

@@

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx8.9$ MK) to Fe XII (formed at $T\approx1.6$ MK) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 1.6$ MK and $8.9$ MK. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.

@@

		\caption{Emission measure ratio as a function of $t_N$ for the single-fluid (left), electron heating (center), and ion heating (right) cases for four different line pairs: Fe XIX/Fe XII (blue), Fe XIX/Fe XV (green), Fe XX/Fe XII (red), and Fe XX/Fe XV (yellow). The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively. The circles ($\beta=0$) and stars ($\beta=1$) indicate the mean EM ratio calculated over all runs for a given $t_N$ (see \autoref{subsec:heating_stats}) and the error bars indicate one standard deviation from the mean.}

@@

	\par \textbf{Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures. \autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding. The circles (stars) correspond to $\beta=0(1)$ and we consider only $\alpha=-2.5$ here. The values of the line ratios can be organized from high to low as Fe XIX/Fe XII, Fe XX/Fe XII, Fe XIX/Fe XV and Fe XX/Fe XV. The second and third pairs have similar ratio values. This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.}

>>>>

\documentclass[preprint]{aastex}

@@

		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated.}

@@

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx8.9$ MK) to Fe XII (formed at $T\approx1.6$ MK) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 1.6$ MK and $8.9$ MK. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun. \textbf{It should be noted that there can be considerable uncertainties in deriving a reliable $\mathrm{EM}(T)$ distribution from observations due to uncertainties from the atomic physics, line-of sight, loop geometry, etc., which will hopefully be mitigated by improved knowledge of such quantities in the future. \citet{guennou_can_2013} provide an extensive overview of this topic.}

@@

		\caption{Emission measure ratio as a function of $t_N$ for the single-fluid (left), electron heating (center), and ion heating (right) cases for four different line pairs: Fe XIX/Fe XII (blue), Fe XIX/Fe XV (green), Fe XX/Fe XII (red), and Fe XX/Fe XV (yellow). The circles ($\beta=0$) and stars ($\beta=1$) indicate the mean EM ratio calculated over all runs for a given $t_N$ (see \autoref{subsec:heating_stats}) and the error bars indicate one standard deviation from the mean. Here we only show the results for $\alpha=-2.5$.}

@@

	\par \textbf{Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures. \autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding. The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively. The circles (stars) correspond to $\beta=0(1)$ and we consider only $\alpha=-2.5$ here. The values of the line ratios can be organized from high to low as Fe XIX/Fe XII, Fe XX/Fe XII, Fe XIX/Fe XV and Fe XX/Fe XV. The second and third pairs have similar ratio values. This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.}
